Tennis doubles and ghosts

### 2022-06-28 inst/tennis.Rmd

s---
title: "Tennis doubles and ghosts"
output: bookdown::html_document2
---

@@

>>>>

---
title: "Tennis doubles and ghosts"
output: bookdown::html_document2
---

@@

### Analysis with `hyper3` {-}

The likelihood for the 9-2 scoreline between $\left\lbrace
p1,p2\right\rbrace$ and $\left\lbrace p3,p4\right\rbrace$ would have a
likelihood function of

$$
\frac{
\left(\lambda p_1 +\lambda p_2\right)^{9}
\left(p_2 + p_3\right)^{2}
}{
\left(\lambda p_1 +\lambda p_2+p_2 + p_3\right)^{11}
}
$$

```{r printH}
H3 <- as.hyper3(H)
H3

## 1&2 vs 3&4;  scoreline 9-2 (again), with lambda=1.2

f <- function(lambda){
  H3[c(p1=lambda,p2=lambda)] %<>% inc(9)
  H3[c(p3=1,p2=1)] %<>% dec(2)
  H3[c(p1=lambda,p2=lambda,p3=1,p2=1)] %<>% dec(11)
  return(H3)
}
f(1.1443345)
f(1.888888)
```

maximize:

```{r,maxH3,cache=TRUE}
tennis_H3_maxp <- maxp(H3)
tennis_H3_maxp
```

Compare the `hyper2` evaluates:

```{r}
tennis_maxp
tennis_ghost_maxp
```
